---
title: "Cabbages"
author: "Sarah Medina"
date: "Fall 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
 
 
 
 The box plot demonstrates a statistical difference in the amount of Vitamin C dependent on the cabbage's cultivation method. Method c39 has a median of 51 unlike,method c52 which has a median of 65. Furthermore, if the two boxes were put on to the same column they would not intersect.
 
### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```

The first Quartile of method c52 is at 58
and the third Quartile of method c39 is at
54.75. The first Quartile of c 52 is higher than the third Quartile of c 39 this indicates a statistical difference between the two cultivation methods and the amount of Vitamin C.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
 
 The p value is 0.00000003405. The p value indicates that the possibility of both methods yielding the same amount of Vitamin C is extremely low almost impossible. Therefore, we reject the idea that both cultivation methods yield the same amount of Vitamin C. Method c52 yields more Vitamin C.

# Discussion and Conclusion

The box plot and t test both demonstrated a statistical difference between the two cultivation methods additionally, the p value given by the t test indicated an extremely low possibility that both methods will ever yield the same amount of Vitamin C. Therefore, the cultivation method c 52 will always yield more Vitamin c. 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
